Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-05-12 paper/main.tex

The three main considerations when designing a machine learning workflow for synthetic biology is feature representation, prediction and recommendation algorithms.
We will discuss our workflow in terms of the Design-Build-Learn-Test cycle, where prediction will be discussed in the Design section and feature representation with prediction in the Learn one.\\
Figure \ref{fig: Flowchart} shows the DBTL cycle with the machine learning process emphasised.
Principally, machine learning is used in the LEARN and DESIGN phase and the other two are driven by choices made by human researchers. 
In LEARN phase we use the Gaussian Process regression algorithm to predict the TIR of different RBS sequences and in the DESIGN phase we use the Upper Confidence Bound multi-armed Bandit algorithm to recommend sequences to be Built and Tested next.\\

@@

>>>>

Our experiments followed the Design-Build-Test-Learn cycle methodology.
Figure \ref{fig: Flowchart} shows our DBTL cycle with the machine learning process emphasised.
Principally, machine learning is used in the LEARN and DESIGN phase and the other two are driven by choices made by human researchers. 
In LEARN phase we use the Gaussian Process regression algorithm to predict the TIR of different RBS sequences and in the DESIGN phase we use the Upper Confidence Bound multi-armed Bandit algorithm to recommend sequences to be Built and Tested next.\\

@@

The three main considerations when designing a machine learning workflow for synthetic biology is feature representation, prediction and recommendation algorithms.
We will discuss our workflow in terms of the Design-Build-Learn-Test cycle, where prediction will be discussed in the Design section and feature representation with prediction in the Learn one.\\
